### 2021-02-22 main.tex
Add loss derivative into the appendix
Add some todos

@@

@@

>>>>

\todo[inline]{Related problem: Ranking. See Mohri etc.}

@@

\todo[inline]{Idea for next project: Optimize precedence directly in a RL fashion: Generate precedence and evaluate with Vampire. If it is the best precedence seen so far, loss is 0 and gradient is 0. Otherwise ground truth is the best precedence seen so far on this problem and we use "differentiable ranking" to backpropagate. Possibly with some exploration, e.g. random swaps of pairs of symbols.}

@@

\section{Loss derivative}

The loss is differentiable with respect to the symbol costs:
\begin{align*}
\frac{\partial \loss}{\partial c_i}
&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse}{P})) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
&= (p(\Better{\PrecBetter}{\PrecWorse}{P}) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
\end{align*}

This means that it is possible to backpropagate the loss gradient into the symbol cost model. \todo{MS: tohle bude tezky,
ale ackoliv ML people by tohle uz asi chapali, ATP crowd spis bude
potrebovat obsirnejsi vysvetleni.}
